%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt]{developercv} % Default font size, values from 8-12pt are recommended
%----------------------------------------------------------------------------------------
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta}

\newcommand\score[2]{%
  \pgfmathsetmacro\pgfxa{#1 + 1}%
  \tikzstyle{scorestars}=[star, star points=5, star point ratio=2.25, draw, inner sep=1.3pt, anchor=outer point 3]%
  \begin{tikzpicture}[baseline]
    \foreach \i in {1, ..., #2} {
      \pgfmathparse{\i<=#1 ? "black" : "white"}
      \edef\starcolor{\pgfmathresult}
      \draw (\i*1.75ex, 0) node[name=star\i, scorestars, fill=\starcolor]  {};
   }
  \end{tikzpicture}%
}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Ghazi}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Sultan}}}}} % Last name

\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Bangalore, India}\\
	\icon{Envelope}{12}{\href{mailto:ghazisultan25@gmail.com}{ghazisultan25@gmail.com}}\\
	\icon{GraduationCap}{12}{IIT Kharagpur}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Phone}{12}{+91-8597235010}\\
	\icon{Github}{12}{\href{https://github.com/iamghazi}{github.com/iamghazi}}\\
	\icon{Globe}{12}{\href{https://iamghazi.github.io/}{iamghazi.github.io}}\\
\end{minipage}

\vspace{0.1cm}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\cvsect{Education}
\begin{entrylist}
	\entry
		{2014 - 2019}
		{Integrated M.Sc.}
		{Indian Institute of Technology, Kharagpur}
		{\texttt{Applied Geology}\hfill\texttt{7.8/10.0}}
	\entry
		{2012 - 2014}
		{All India Senior School Certificate Examination}
		{Sadar Alam Memorial Secondary School, Nalanda, Bihar}
		{\texttt{Central Board of Secondary Education}\hfill\texttt{93.2\%}}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\cvsect{Experiences}
\begin{entrylist}
	\entry
		{6/2019 -- Present\\\footnotesize{Full Time}}
		{Software Development Engineer}
		{Idea Rise Technology}
		{• \href{https://agentsdash.com}{\textbf{AgentsDash.com:}} This Django CRM enables companies to measure the performance of real-estate agents, to manage progress of leads and performance of the company as a whole. \\• \textbf{General Purpose CRM:} It includes features like deal categorization in stages, customisation to fit unique sales process, task scheduling, insights and reports, and gmail integration.\\• \textbf{Invest Bihar CRM:} A CRM built from scratch to manage the companies which are interested in investing in Bihar, India. \\• \textbf{Technologies in above CRMs:} \texttt{Python}, \texttt{Django}, \texttt{JavaScript}, \texttt{Jquery}, \texttt{Git}, \texttt{DataTables}, \texttt{HightCharts}, \texttt{Nginx}. \\ • Developed a dashboard for clean and error-free spreadsheet data management using Google App Script.\\ • Wrote GAS scripts to facilitate two-way data-flow between XERO, Facebook \& Google spreadsheets.}
	\entry
		{2/2020 \\\footnotesize{Contract | Remote}}
		{Full-Stack Developer}
		{Sneed Technologies Pvt. Ltd.}
		{• Integration of Backend and Frontend. Technology used: \texttt{React}, \texttt{Nuxt.js}, \texttt{Node.js}, \texttt{Express}, \texttt{MongoDB}}
	\entry
		{7/2015 -- Present\\\footnotesize{Part Time | Remote}}
		{Contributor}
		{Slader LLC}
		{• Provided solutions for around 300 \texttt{Java} problems, 150 \texttt{C++} problems and 1500+ \texttt{Mathematics} problems.}
	\entry
		{5/2018 -- 7/2018\\\footnotesize{Internship}}
		{Backend Developer}
		{Power2SME Private Limited}
		{• Developed a wrapper API on top of two third party APIs \texttt{APIWHA} \& \texttt{WABOXAPP} to automate company-client interaction via WhatsApp. Deployed and tested the API by sending transaction receipt to the clients.}
	\entry
		{5/2017 -- 7/2017\\\footnotesize{Remote Internship}}
		{Backend Developer}
		{Mrittica Infotech Private Limited}
		{• Developed admin dashboard from scratch for an E-commerce startup which sell organic products. Created the relational database and developed the backend of its android app in a team of two.}
	\entry
		{10/2015 -- 1/2017}
		{Web Team Lead}
		{Prithvi | IIT Kharagpur}
		{• Lead a team of 3 to develop and manage the official website of Prithvi - 2017, an annual departmental fest of the department of Geology \& Geophysics, IIT Kharagpur.}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
	\entry
		{1/2020 \\\footnotesize{Self Project}}
		{Customised Data Table}
		{DataTables}
		{---Developed beautiful data table with category filters and column selector using jQuery DataTables Plug-in}
	\entry
		{9/2019 \\\footnotesize{Self Project}}
		{Diary Application}
		{Django}
		{---Django Application with signup, login, email confirmation and CRUD operations support on Diary Entries.}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\cvsect{Skills}

\begin{minipage}[t]{1\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
\textbf{Languages:} \texttt{Python \score{4}{5}  | Javascript \score{4}{5}  | C++ \score{5}{5}  | Java \score{4}{5}  | PHP \score{3}{5}  | HTML \score{5}{5}} \\ 
\textbf{Frameworks \& Libraries:} \texttt{Django \score{4}{5}  | Jquery \score{4}{5}  | Google App Script (GAS) \score{4}{5}} \\
\textbf{Miscellaneous:} \texttt{Git \score{4}{5}  | MySQL \score{4}{5}  | Atom \score{4}{5}  | CSS \score{5}{5}  | Linux \score{4}{5}  | Bootstrap \score{5}{5}} \\
\textbf{Experienced:}\texttt{Node.js | Express | React | Nuxt.js | MongoDB | Mongoose | CGI | Spring Framework | Eclipse | JUnit | OAuth | RStudio | MATLAB | Xero API | Facebook API}% Dummy text
\end{minipage}\\
%-----------------------------------------------------------------------------------
% Courses and skills
%-----------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Relevant Coursework}
	
	Programming \& Data Structures, Design \& Analysis of Algorithms, Computer Networks, Probability \& Statistics.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{M.Sc. Thesis Project}
	
	Developed a \textbf{Mathematical model} and wrote \textbf{R scripts} to correlate groundwater and river water fluctuation
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Achievements}
	
	Ranked among top \textbf{1\%} students in \textbf{JEE Mains} and secured \textbf{AIR 6714} in \textbf{JEE Advanced}.
\end{minipage}
\\
%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - Fluent\\
	\textbf{Urdu/Hindi} - Native Speaker\\
	\textbf{Bhojpuri} - Native Speaker
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	Playing Badminton \& Chess.	Swimming. Running. Reading History, Philosophy \& Psychology.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Extra Curricular Activities}
	
	Organized and took part in several programs such as Blood Donation Camps, Sadbhavana Run, etc. as NCC Cadet.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
